Effect of quality-adjusted production function inputs

### 2015-05-10 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including tilde on João's name.

\author[IST]{João dos Santos}
\author[Leeds]{Paul Brockway}
\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
\ead{mkh2@calvin.edu}
\author[Leeds]{Marco Sekai}
\author[IST]{Tiago Domingos}
\author[Leeds]{Julia Steinberger}

@@

>>>>

\author[IST]{Jo\~{a}o dos Santos}
\author[Leeds]{Paul Brockway}
\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
\ead{mkh2@calvin.edu}
\author[Leeds]{Marco Sekai}
\author[IST]{Tiago Domingos}
\author[Leeds]{Julia Steinberger}

@@

# Lists
y <- NULL
k <- NULL
l <- NULL
e <- NULL
t <- NULL
f <- NULL
# Economic output
y$PT <- substitute(iGDP)
y$UK <- substitute(iGDP)
# Portugal undajusted inputs
k$PT$unadj <- substitute(iKstkS.L)
l$PT$unadj <- substitute(iL)
e$PT$unadj <- substitute(iXpMP)
# Portugal quality-adjusted inputs
k$PT$adj <- substitute(iKservS.L)
l$PT$adj <- substitute(ihLest)
e$PT$adj <- substitute(iUMP)
# UK unadjusted inputs
k$UK$unadj <- substitute(iKstkO.WwithRD)
l$UK$unadj <- substitute(iL)
e$UK$unadj <- substitute(iXp)
# UK quality-adjusted inputs
k$UK$adj <- substitute(iKservO.WwithRD)
l$UK$adj <- substitute(ihLest)
e$UK$adj <- substitute(iU)
# Time variables
t$PT <- substitute(iYear)
t$UK <- substitute(iYear)

# countries <- c(substitute(PT), substitute(UK))
# adjusteds <- c(substitute(unadj), substitute(adj))
# energies <- c(substitute(noE), substitute(withE))
# 
# for (country in countries){
#   for (adjusted in adjusteds){
#     for (energy in energies){
#       substitute(f$country$adjusted$energy, 
#                  list(country=country, adjusted=adjusted, energy=energy)) <- "a"
#     }
#   }
# }
